Energy and the CES production function

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including two tables for nest-aware sigmas.

**** Is there a graph we want to make here? ---MKH ****
%
<<CES_sigma, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES") %>% 
           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%

>>>>

**** Is there a graph we want to make here? ---MKH ****
%
<<CES_sigma, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES") %>% 
           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
         caption="Factor substitution~($\\sigma$) for CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_inner, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES") %>% 
           select(Country, model, flavor, energy, nest, CSP, sigma_12, sigma_23, sigma_13),
         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
%
<<CES_sigma_nest_aware_outer, results="asis">>=
myXTable(filter(AllCoeffs, model=="CES") %>% 
           select(Country, model, flavor, energy, nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2),
         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
